Data Descriptor: Corresponding author journal publishing activities 2014-2018

### 2019-10-21 analysis/paper.Rmd
fix wording

```{r}
top_10_publisher <- rp_df %>%
  filter(oa_journal == FALSE) %>%
  group_by(publisher) %>%
  summarise(n = sum(n_publications)) %>%
  arrange(desc(n)) %>%
  head(11) %>%
  .$publisher
top_10_countries <- rp_df %>%
  filter(oa_journal == FALSE) %>%
  group_by(country_code) %>%
  summarise(n = sum(n_publications)) %>%
  arrange(desc(n)) %>%
  head(10) %>%
  .$country_code
plot_df <- rp_df %>%
  filter(oa_journal == FALSE) %>%
  mutate(fct_publisher = ifelse(publisher %in% top_10_publisher, publisher, "Others")) %>%
  mutate(fct_publisher = ifelse(is.na(fct_publisher), "Others", fct_publisher)) %>%
  mutate(fct_countrcode = ifelse(country_code %in% top_10_countries, country_code, "Others")) %>%
  mutate(fct_countrcode = factor(fct_countrcode, levels = c(top_10_countries, "Others"))) %>%
  group_by(fct_publisher, fct_countrcode) %>%
  summarize(n = sum(n_publications)) %>%
  mutate(prop = n / sum(n)) %>%
  ungroup()
#' plot
ggplot(plot_df, aes(forcats::fct_rev(fct_countrcode), prop, fill = prop)) +
  coord_flip() +
  geom_bar(stat = "identity") +
  facet_wrap(~ fct_relevel(fct_publisher, top_10_publisher), ncol = 3) +
  scale_fill_viridis_c(
    "Country share per publisher (in %)",
    labels = scales::percent_format(accuracy = 5L),
    option = "C"
  ) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 5L))  +
  labs(
    title = "Who did publish in subscription-based journals from major publishers between 2014 - 2018?",
    x = "Country of Affiliation (Top 10)",
    y = "Share of Original Articles and Reviews per Publisher",
    caption = "Data Sources:  Web of Science in-house database Competence Centre for Bibliometrics for German Science.
    Publisher names were disambiguated using Crossref metadata. OA status obtained from the Bielefeld GOLD OA list.
    Funding: Federal Ministry of Education and Research of Germany (BMBF), Project OAUNI (01PU17023A)",
    subtitle = "Corresponding authors' countries of affiliation per publisher."
  ) +
  theme_minimal(base_family = "Roboto", base_size = 16) +
  theme(plot.margin = margin(30, 10, 30, 10)) +
  theme(panel.grid.minor.y = element_blank()) +
  theme(axis.ticks = element_blank()) +
  theme(panel.grid.major.y = element_blank()) +
  theme(panel.border = element_blank()) +
  theme(
    legend.position = "top",
    legend.justification = "right",
    legend.text = element_text(size =  9)
  ) -> p
#' save as png
ggsave(
  "figure/publisher_share.png",
  p,
  dpi = 450,
  height = 13,
  width = 17
)
```

>>>>

```{r}
top_10_publisher <- rp_df %>%
  filter(oa_journal == FALSE) %>%
  group_by(publisher) %>%
  summarise(n = sum(n_publications)) %>%
  arrange(desc(n)) %>%
  head(11) %>%
  .$publisher
top_10_countries <- rp_df %>%
  filter(oa_journal == FALSE) %>%
  group_by(country_code) %>%
  summarise(n = sum(n_publications)) %>%
  arrange(desc(n)) %>%
  head(10) %>%
  .$country_code
plot_df <- rp_df %>%
  filter(oa_journal == FALSE) %>%
  mutate(fct_publisher = ifelse(publisher %in% top_10_publisher, publisher, "Others")) %>%
  mutate(fct_publisher = ifelse(is.na(fct_publisher), "Others", fct_publisher)) %>%
  mutate(fct_countrcode = ifelse(country_code %in% top_10_countries, country_code, "Others")) %>%
  mutate(fct_countrcode = factor(fct_countrcode, levels = c(top_10_countries, "Others"))) %>%
  group_by(fct_publisher, fct_countrcode) %>%
  summarize(n = sum(n_publications)) %>%
  mutate(prop = n / sum(n)) %>%
  ungroup()
#' plot
ggplot(plot_df, aes(forcats::fct_rev(fct_countrcode), prop, fill = prop)) +
  coord_flip() +
  geom_bar(stat = "identity") +
  facet_wrap(~ fct_relevel(fct_publisher, top_10_publisher), ncol = 3) +
  scale_fill_viridis_c(
    "Country share per publisher (in %)",
    labels = scales::percent_format(accuracy = 5L),
    option = "C"
  ) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 5L))  +
  labs(
    title = "Who published in subscription-based journals from major publishers between 2014 - 2018?",
    x = "Country of Affiliation (Top 10)",
    y = "Share of Original Articles and Reviews per Publisher",
    caption = "Data Sources:  Web of Science in-house database Competence Centre for Bibliometrics for German Science.
    Publisher names were disambiguated using Crossref metadata. OA status obtained from the Bielefeld GOLD OA list.
    Funding: Federal Ministry of Education and Research of Germany (BMBF), Project OAUNI (01PU17023A)",
    subtitle = "Corresponding authors' countries of affiliation per publisher."
  ) +
  theme_minimal(base_family = "Roboto", base_size = 16) +
  theme(plot.margin = margin(30, 10, 30, 10)) +
  theme(panel.grid.minor.y = element_blank()) +
  theme(axis.ticks = element_blank()) +
  theme(panel.grid.major.y = element_blank()) +
  theme(panel.border = element_blank()) +
  theme(
    legend.position = "top",
    legend.justification = "right",
    legend.text = element_text(size =  9)
  ) -> p
#' save as png
ggsave(
  "figure/publisher_share.png",
  p,
  dpi = 450,
  height = 13,
  width = 17
)
```
